Concurrent Programming with CXL

### 2020-06-06 book/paper.tex
fix

Consider a variant of the Dining Philosophers (which were clearly Dutch---who
else need two forks to eat a meal?) that I call Italian Philosophers (who only
need one fork each to eat spaghetti).  Again, there are five philosophers.
This time, however, there is a glass sitting in the middle of the table with only
three forks in it.  A philosopher needs one of those forks to eat, but clearly,
no more than three philosophers can eat at a time.

>>>>

Consider a variant of the Dining Philosophers (which were clearly Dutch---who
else need two forks to eat a meal?) that we call Italian Philosophers (who only
need one fork each to eat spaghetti).  Again, there are five philosophers.
This time, however, there is a glass sitting in the middle of the table with only
three forks in it.  A philosopher needs one of those forks to eat, but clearly,
no more than three philosophers can eat at a time.
